%
% File acl2016.tex
%
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Csc 655 Final Report}

\author{Rebecca Shartp, Aditya Kousik, Enrique Noriega, Benjamin Martin\\
  {\tt \{bsharp,akousyk,enoriega,bamartin\}@email.arizona.edu} \\}
 
\date{}

%\author{Enrique Noriega \\
%{\tt enoriega@email.arizona.edu} \\\And
%Rebecca Sharp \\
%{\tt bsharp@email.arizona.edu} \\\And
%Aditya Kousik \\
%{\tt adityak@email.arizona.edu} \\\And
%Benjamin Martin \\
%{\tt bamartin@email.arizona.edu} 
%}

\begin{document}
\maketitle
\begin{abstract}
  
\end{abstract}

\section{Introduction}

Question Answering (QA) is a challenging problem. Systems attempting to solve the problem still don't achieve performance comparable to a human. there are multiple reasons for this. One of them is that many questions require \emph{soft inference}, where traditional information retrieval methods fail. Another reason is that training data is scarce, and coming up with more training data is expensive and requires a lot of effort. \\

During the course of Spring 16, we pursued some ideas to tackle these two issues. At the end we compare how well the solutions work and do an ensemble model to see how well parallel efforts complement with each other. The code implementing our ideas can be found at:\\ 
\url{https://github.com/enoriega/cs665.git}\\

To do evaluation of our system and our ideas, we use the \emph{AI2 dataset} from its Kaggle challenge.
\input{enrique.tex}

\input{aditya.tex}

\input{ben.tex}

\input{becky.tex}

\section{Conclusions}

%\bibliography{acl2016}
%\bibliographystyle{acl2016}

\end{document}
